\documentclass{article}

\usepackage[margin=1.25in]{geometry}

\usepackage[utf8]{inputenc}

\usepackage[T1]{fontenc}

\usepackage[english]{babel}

\usepackage{enumitem}

\usepackage{titlesec}

\usepackage{fancyhdr}

\usepackage{xcolor}

\usepackage{hyperref}

\usepackage{setspace}

\usepackage{parskip}

\date{\today}

\begin{document}


\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize\textcolor{gray}{Mutual Non-Disclosure Agreement --- Brooks / \_\_\_\_\_\_\_\_\_\_\_\_ \hfill Page \thepage}}

\titleformat{\section}{\normalfont\bfseries\MakeUppercase}{}{0em}{}
\titleformat{\subsection}{\normalfont\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{1.5em}{0.5em}
\titlespacing*{\subsection}{0pt}{1em}{0.25em}

\setstretch{1.15}

\begin{center}
{\Large\bfseries MUTUAL NON-DISCLOSURE AGREEMENT}
\end{center}

\vspace{1em}

This Mutual Non-Disclosure Agreement (``Agreement'') is entered into as of the date last signed below (``Effective Date'') by and between:

\begin{quote}
\textbf{Daniel Brooks}, an individual residing in Boston, Massachusetts (``Disclosing Party'' or ``Brooks''), and

\textbf{\rule{8cm}{0.4pt}}, an individual or entity with a principal place of business or residence at \rule{8cm}{0.4pt} (``Receiving Party'').
\end{quote}

Each party may act as both a disclosing party and a receiving party under this Agreement. Together, Brooks and the Receiving Party are referred to herein as the ``Parties.''

\section{Recitals}

WHEREAS, Brooks has developed a proprietary algorithmic trading system (the ``System'') that operates on prediction market platforms including Polymarket, incorporating a multi-model artificial intelligence consensus approach, a novel signal generation methodology, and related software, data, and infrastructure;

WHEREAS, the Parties desire to explore a potential business relationship, investment, collaboration, or employment arrangement (the ``Purpose'') that may require the disclosure of Confidential Information, as defined herein;

WHEREAS, each Party desires to protect its respective Confidential Information from unauthorized disclosure or use;

NOW, THEREFORE, in consideration of the mutual covenants and obligations set forth herein, and for other good and valuable consideration, the receipt and sufficiency of which are hereby acknowledged, the Parties agree as follows:

\section{1. Definitions}

\subsection{1.1 Confidential Information}

``Confidential Information'' means any and all non-public information, data, materials, or knowledge disclosed by one Party (the ``Discloser'') to the other Party (the ``Recipient''), whether disclosed orally, in writing, electronically, visually, or by any other means, that is designated as confidential at the time of disclosure or that reasonably should be understood to be confidential given the nature of the information and the circumstances of disclosure. Without limiting the foregoing, Confidential Information of Brooks specifically includes, but is not limited to:

\begin{enumerate}[label=(\alph*), leftmargin=2em]
\item \textbf{Trading Strategy.} The multi-model large language model (LLM) consensus methodology used to generate probability estimates for prediction market outcomes, including the use of Claude (Anthropic), GPT-4o (OpenAI), Gemini (Google), Grok-3 (xAI), and DeepSeek, the specific methods by which model outputs are aggregated or weighted, the outlier exclusion and filtering logic applied to model consensus outputs, edge calculation formulas, trade signal generation thresholds, and any modifications, refinements, or extensions of the foregoing.

\item \textbf{Software and Codebase.} All source code, object code, scripts, algorithms, modules, libraries, application programming interface (API) integration layers, data pipeline configurations, system architecture designs, data schemas, database structures, workflow automation logic, and any related technical documentation, whether in draft or final form, pertaining to the System.

\item \textbf{Trading Data.} Historical trade signal records, win rates, expected value and edge calculations, portfolio performance metrics, model calibration datasets, backtesting results, probability estimates, position sizing history, and any derived analytics or reporting generated from operation of the System.

\item \textbf{Infrastructure.} Server configurations, cloud deployment architecture, API credential structures and access management approaches, environment configurations, deployment scripts, network topology, monitoring and alerting setups, and any other technical infrastructure supporting the operation of the System.

\item \textbf{Business Information.} Any business plans, financial projections, investor materials, potential partnership discussions, pricing strategies, and competitive analyses related to the System.
\end{enumerate}

\subsection{1.2 Exclusions}

``Confidential Information'' does not include information that the Recipient can demonstrate by clear and convincing written evidence:

\begin{enumerate}[label=(\alph*), leftmargin=2em]
\item was in the public domain at the time of disclosure or subsequently enters the public domain through no act or omission of the Recipient;

\item was rightfully known to the Recipient prior to disclosure by the Discloser, without any obligation of confidentiality;

\item was independently developed by the Recipient without use of or reference to any Confidential Information of the Discloser, as evidenced by contemporaneous written records;

\item was rightfully received by the Recipient from a third party without restriction on disclosure; or

\item is required to be disclosed by applicable law, regulation, court order, or governmental authority, provided that the Recipient gives the Discloser prompt written notice of such requirement prior to disclosure (to the extent permitted by law) and cooperates with the Discloser in seeking a protective order or other appropriate relief.
\end{enumerate}

\section{2. Obligations of Confidentiality}

\textbf{2.1 Non-Disclosure.} Each Recipient agrees to hold the Discloser's Confidential Information in strict confidence and not to disclose any Confidential Information to any third party without the prior written consent of the Discloser, except as expressly permitted by this Agreement.

\textbf{2.2 Non-Use.} Each Recipient agrees not to use any Confidential Information of the Discloser for any purpose other than evaluating or pursuing the Purpose described in the Recitals above. Without limiting the foregoing, the Receiving Party shall not use any Confidential Information of Brooks to develop, enhance, or assist in developing any competing algorithmic trading system, prediction market trading strategy, or related product or service.

\textbf{2.3 Standard of Care.} Each Recipient agrees to protect the Discloser's Confidential Information using at least the same degree of care used to protect its own confidential information of similar nature and importance, but in no event less than reasonable care.

\textbf{2.4 Limited Access.} Each Recipient agrees to limit access to the Discloser's Confidential Information to its employees, agents, advisors, and representatives who have a legitimate need to know such information for the Purpose and who are bound by written confidentiality obligations at least as protective as those set forth in this Agreement.

\textbf{2.5 Notification of Breach.} Each Recipient agrees to notify the Discloser promptly in writing upon becoming aware of any unauthorized use, disclosure, or access to Confidential Information, and to cooperate fully with the Discloser in mitigating any resulting harm.

\section{3. Non-Reverse-Engineering}

\textbf{3.1 Prohibition.} The Receiving Party shall not, and shall not permit any third party to, directly or indirectly:

\begin{enumerate}[label=(\alph*), leftmargin=2em]
\item reverse engineer, decompile, disassemble, or otherwise attempt to derive the source code, underlying algorithms, models, logic, or architecture of the System or its components;

\item attempt to reconstruct, replicate, or independently derive the Trading Strategy or any material component thereof from observation of the System's outputs, trade signals, or performance data;

\item use statistical analysis, machine learning, or any other method to infer, approximate, or recreate any aspect of the Trading Strategy, Codebase, or model weighting methodology from disclosed Trading Data or observable behavior of the System.
\end{enumerate}

\textbf{3.2 No License.} Nothing in this Agreement grants the Receiving Party any license, right, title, or interest in or to any Confidential Information of Brooks, including any intellectual property rights therein, beyond the limited right to review such information solely for the Purpose.

\section{4. Non-Compete}

\textbf{4.1 Scope.} In consideration of access to Brooks's Confidential Information, including the Trading Strategy and related Codebase and Trading Data, the Receiving Party agrees that, during the term of this Agreement and for a period of twelve (12) months following the later of (a) the termination or expiration of this Agreement, or (b) the last date on which Confidential Information of Brooks was disclosed to the Receiving Party (``Non-Compete Period''), the Receiving Party shall not, directly or indirectly:

\begin{enumerate}[label=(\alph*), leftmargin=2em]
\item develop, build, operate, invest in, advise, or provide material assistance to any algorithmic trading system, bot, or automated strategy that operates primarily on prediction market platforms (including but not limited to Polymarket, Manifold Markets, Kalshi, or any substantially similar platform);

\item use any component of the Trading Strategy, including the multi-model LLM consensus framework, outlier exclusion methodology, or edge-based signal generation approach, in any trading system, product, or service, whether operated on a prediction market platform or otherwise.
\end{enumerate}

\textbf{4.2 Reasonableness.} The Parties acknowledge that the scope, duration, and geographic reach of the non-compete restriction set forth in Section 4.1 are reasonable and necessary to protect Brooks's legitimate business interests, given the highly specialized nature of the Trading Strategy and the narrow market for prediction market algorithmic trading systems.

\textbf{4.3 Severability of Non-Compete.} If any court of competent jurisdiction determines that any provision of Section 4.1 is unenforceable as written, the Parties authorize such court to modify the provision to the minimum extent necessary to make it enforceable, and the remaining provisions of this Agreement shall continue in full force and effect.

\smallskip
\noindent\textit{Note: The non-compete provision in this Section 4 applies only to the Receiving Party, not to Brooks, reflecting the asymmetric nature of the proprietary information being protected.}

\section{5. Return or Destruction of Information}

\textbf{5.1} Upon written request by the Discloser, or upon termination or expiration of this Agreement, the Recipient shall promptly return or destroy (at the Discloser's election) all tangible and electronic materials containing Confidential Information of the Discloser, including all copies, summaries, extracts, and derivative works thereof. The Recipient shall certify in writing that such return or destruction has been completed within ten (10) business days of such request.

\textbf{5.2} Notwithstanding Section 5.1, the Recipient may retain one archival copy of Confidential Information solely to the extent required by applicable law or regulation, provided such copy remains subject to the confidentiality obligations of this Agreement.

\section{6. Term and Survival}

\textbf{6.1 Term.} This Agreement shall commence on the Effective Date and shall continue for a period of two (2) years, unless earlier terminated by either Party upon thirty (30) days' written notice to the other Party.

\textbf{6.2 Confidentiality Obligations.} The confidentiality and non-use obligations set forth in Section 2 shall survive the expiration or termination of this Agreement for a period of two (2) years from the date of each disclosure of Confidential Information, or from the date of termination of this Agreement, whichever is later.

\textbf{6.3 Survival of Other Provisions.} Sections 3 (Non-Reverse-Engineering), 4 (Non-Compete), 5 (Return or Destruction), 7 (Ownership), 8 (Remedies), 9 (Disclaimer), and 11 (General Provisions) shall survive the expiration or termination of this Agreement in accordance with their terms.

\section{7. Ownership of Confidential Information}

\textbf{7.1} All Confidential Information disclosed by a Discloser shall remain the sole and exclusive property of the Discloser. Disclosure of Confidential Information under this Agreement shall not be construed as granting the Recipient any right, license, or interest in or to such Confidential Information, or any patent, copyright, trademark, trade secret, or other intellectual property right of the Discloser, whether by implication, estoppel, or otherwise.

\textbf{7.2} The Parties acknowledge that Brooks retains all right, title, and interest in and to the Trading Strategy, Codebase, Trading Data, and Infrastructure as described in Section 1.1, and that such assets constitute valuable trade secrets protected under applicable federal and Massachusetts law, including the Defend Trade Secrets Act, 18 U.S.C. \S~1836 \textit{et seq.}, and the Massachusetts Uniform Trade Secrets Act, M.G.L. c.~93, \S~42 \textit{et seq.}

\section{8. Remedies}

\textbf{8.1 Acknowledgment of Irreparable Harm.} The Parties acknowledge that any breach or threatened breach of this Agreement would cause immediate and irreparable harm to the Discloser for which monetary damages would be an inadequate remedy, and that the Discloser would not have an adequate remedy at law.

\textbf{8.2 Equitable Relief.} Accordingly, in the event of any breach or threatened breach of this Agreement, the Discloser shall be entitled to seek immediate equitable relief, including specific performance and injunctive relief, without the necessity of proving actual damages or posting bond, in addition to any other rights and remedies available at law or in equity.

\textbf{8.3 Damages.} Nothing in this Section 8 shall limit the right of the Discloser to seek monetary damages, including consequential, incidental, and punitive damages to the extent permitted by applicable law, for any breach of this Agreement.

\textbf{8.4 Attorneys' Fees.} In any legal proceeding arising out of or relating to this Agreement, the prevailing Party shall be entitled to recover its reasonable attorneys' fees, costs, and expenses from the non-prevailing Party.

\section{9. Disclaimer of Warranties}

\textbf{9.1} All Confidential Information is provided ``AS IS.'' The Discloser makes no representations or warranties, express or implied, as to the accuracy, completeness, fitness for a particular purpose, or non-infringement of any Confidential Information. The Recipient assumes all risk associated with its use of Confidential Information for evaluation purposes.

\textbf{9.2} Neither Party warrants that any business relationship, transaction, or agreement will result from the disclosure of Confidential Information or the discussions contemplated by this Agreement.

\section{10. No Obligation to Proceed}

Nothing in this Agreement shall obligate either Party to disclose any particular Confidential Information, to enter into any further agreement, to consummate any transaction, or to continue any discussions or negotiations with the other Party. Either Party may terminate discussions at any time without liability to the other Party, except as expressly provided herein.

\section{11. General Provisions}

\textbf{11.1 Governing Law.} This Agreement shall be governed by and construed in accordance with the laws of the Commonwealth of Massachusetts, without regard to its conflict of laws principles.

\textbf{11.2 Dispute Resolution.} Any dispute, claim, or controversy arising out of or relating to this Agreement, or the breach, termination, or validity thereof, shall be resolved exclusively in the state or federal courts of competent jurisdiction located in Suffolk County, Massachusetts. Each Party hereby irrevocably submits to the personal jurisdiction of such courts and waives any objection to venue therein.

\textbf{11.3 Entire Agreement.} This Agreement constitutes the entire agreement between the Parties with respect to the subject matter hereof and supersedes all prior and contemporaneous discussions, understandings, and agreements, whether written or oral, relating to the same subject matter.

\textbf{11.4 Amendments.} This Agreement may not be amended or modified except by a written instrument signed by both Parties.

\textbf{11.5 Waiver.} No failure or delay by either Party in exercising any right under this Agreement shall operate as a waiver of that right, nor shall any single or partial exercise of any right preclude any other or further exercise of that right or the exercise of any other right.

\textbf{11.6 Severability.} If any provision of this Agreement is found to be invalid, illegal, or unenforceable under applicable law, such provision shall be modified to the minimum extent necessary to make it valid and enforceable, and the remaining provisions shall continue in full force and effect.

\textbf{11.7 Assignment.} Neither Party may assign this Agreement or any rights or obligations hereunder without the prior written consent of the other Party, except that Brooks may assign this Agreement in connection with a merger, acquisition, reorganization, or sale of all or substantially all of his assets related to the System without such consent. Any purported assignment in violation of this Section shall be null and void.

\textbf{11.8 Counterparts and Electronic Signatures.} This Agreement may be executed in one or more counterparts, each of which shall be deemed an original, and all of which together shall constitute one and the same instrument. Electronic signatures shall be deemed valid and binding to the same extent as original signatures.

\textbf{11.9 Notices.} All notices required or permitted under this Agreement shall be in writing and shall be deemed delivered when sent via email with confirmation of receipt, or when delivered personally, or three (3) business days after being sent by certified mail, return receipt requested, to the addresses set forth in this Agreement or such other address as a Party may designate in writing.

\textbf{11.10 Construction.} This Agreement has been negotiated by the Parties, and its language shall not be construed for or against either Party. Headings are included for convenience only and shall not affect the interpretation of this Agreement.

\vspace{2em}
\begin{center}
\rule{12cm}{0.4pt}
\end{center}
\vspace{1em}

\noindent IN WITNESS WHEREOF, the Parties have executed this Mutual Non-Disclosure Agreement as of the date last written below.

\vspace{2em}

\noindent
\begin{minipage}[t]{0.45\textwidth}
\textbf{DANIEL BROOKS}

\vspace{2em}
\noindent Signature: \rule{5cm}{0.4pt}

\vspace{1em}
\noindent Printed Name: Daniel Brooks

\vspace{1em}
\noindent Date: \rule{5cm}{0.4pt}

\vspace{1em}
\noindent Address: Boston, Massachusetts

\vspace{1em}
\noindent Email: \rule{5cm}{0.4pt}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\textbf{RECEIVING PARTY}

\vspace{2em}
\noindent Signature: \rule{5cm}{0.4pt}

\vspace{1em}
\noindent Printed Name: \rule{4cm}{0.4pt}

\vspace{1em}
\noindent Date: \rule{5cm}{0.4pt}

\vspace{1em}
\noindent Address: \rule{5cm}{0.4pt}

\vspace{1em}
\noindent Email: \rule{5cm}{0.4pt}
\end{minipage}

\newpage

\begin{center}
{\large\bfseries EXHIBIT A: DISCLOSURE LOG}
\end{center}

\vspace{0.5em}
\noindent\textit{To be completed and signed by both Parties at the time of each material disclosure. Attach additional pages as needed.}

\vspace{2em}

\noindent Date of Disclosure: \rule{10cm}{0.4pt}

\vspace{1.5em}
\noindent Description of Information Disclosed:

\vspace{0.5em}
\noindent\rule{\textwidth}{0.4pt}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}

\vspace{1.5em}
\noindent Format of Disclosure (oral / written / electronic / demonstration): \rule{5cm}{0.4pt}

\vspace{1.5em}
\noindent Disclosed by: \rule{10cm}{0.4pt}

\vspace{1.5em}
\noindent Received by: \rule{10cm}{0.4pt}

\vspace{2em}
\noindent
\begin{minipage}[t]{0.45\textwidth}
Discloser Initials: \rule{2cm}{0.4pt}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
Recipient Initials: \rule{2cm}{0.4pt}
\end{minipage}


\end{document}